---
title: "TwitterAnalysis"
author: "nsardar"
date: '2022-07-23'
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Loading the libraries

```{r message=FALSE}
options(scipen = 999) #avoid the scientific notation
library(twitteR)
library(writexl)
library(bitops)
library(tidytext)
library(devtools)
library(sentiment)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)

```

### Getting Data 

Based on the tweets from 4  different mobile manufacturing companies and then we will be doing text analysis and visualization for this companies.

We will be using twitter developer portal to get acces to tweets from twitter website.


```{r message=FALSE}

consumer_key = "3N1fyHxwhVAVs5BCXzuQ8vbXV"
consumer_secret = "IVf6acHFxRWVQ006HNlDP9hygzOXx1XkZdKF9cMZlbL717AIQu"
access_token = "1458218683017347078-UTwl4ULAneM8wgDJypPXsU2KNhI8pU"
acess_token_secret = "4mLTYRLgJHSEoeV3qdz10WT7NdjwOH95AgvA8QCULhr0e"

setup_twitter_oauth(consumer_key,consumer_secret,access_token,acess_token_secret)
```

### Mobile Companies 

We will be using data from the below mentioned companies :
1) Motorola
2) Xiaomi
3) Oneplus
4) Samsung

```{r message=FALSE }


tweetsMotorola = userTimeline('MotorolaUS', n = 1000)
tweetsXiaomi = userTimeline('Xiaomi', n = 1000)
tweetsOnePlus = userTimeline('oneplus', n = 1000)
tweetsSamsung = userTimeline('SamsungMobile', n = 1000)


tweetsDfMotorola = twListToDF(tweetsMotorola)
head(tweetsDfMotorola,2)
tweetsDfXiaomi = twListToDF(tweetsXiaomi)
head(tweetsDfXiaomi,2)
tweetsDfOnePlus = twListToDF(tweetsOnePlus)
head(tweetsDfOnePlus,2)
tweetsDfSamsung = twListToDF(tweetsSamsung)
head(tweetsDfSamsung,2)

```

### Sentiment Analysis 

#### The below score indicates whether the tweets are positive , negative or neutral
#### 4 Positive
#### 2 Neutral
#### 0 Negative

```{r message=FALSE}
finalExtractedTweets = rbind(tweetsDfMotorola, tweetsDfXiaomi, tweetsDfOnePlus, tweetsDfSamsung)

encodeSource <- function(x) {
  if(x=="<a href=\"http://twitter.com/download/iphone\" rel=\"nofollow\">Twitter for iPhone</a>"){
    gsub("<a href=\"http://twitter.com/download/iphone\" rel=\"nofollow\">Twitter for iPhone</a>", "iphone", x,fixed=TRUE)
  }else if(x=="<a href=\"http://twitter.com/#!/download/ipad\" rel=\"nofollow\">Twitter for iPad</a>"){
    gsub("<a href=\"http://twitter.com/#!/download/ipad\" rel=\"nofollow\">Twitter for iPad</a>","ipad",x,fixed=TRUE)
  }else if(x=="<a href=\"http://twitter.com/download/android\" rel=\"nofollow\">Twitter for Android</a>"){
    gsub("<a href=\"http://twitter.com/download/android\" rel=\"nofollow\">Twitter for Android</a>","android",x,fixed=TRUE)
  } else if(x=="<a href=\"http://twitter.com\" rel=\"nofollow\">Twitter Web Client</a>"){
    gsub("<a href=\"http://twitter.com\" rel=\"nofollow\">Twitter Web Client</a>","Web",x,fixed=TRUE)
  } else if(x=="<a href=\"http://www.twitter.com\" rel=\"nofollow\">Twitter for Windows Phone</a>"){
    gsub("<a href=\"http://www.twitter.com\" rel=\"nofollow\">Twitter for Windows Phone</a>","windows phone",x,fixed=TRUE)
  }else if(x=="<a href=\"http://dlvr.it\" rel=\"nofollow\">dlvr.it</a>"){
    gsub("<a href=\"http://dlvr.it\" rel=\"nofollow\">dlvr.it</a>","dlvr.it",x,fixed=TRUE)
  }else if(x=="<a href=\"http://ifttt.com\" rel=\"nofollow\">IFTTT</a>"){
    gsub("<a href=\"http://ifttt.com\" rel=\"nofollow\">IFTTT</a>","ifttt",x,fixed=TRUE)
  }else if(x=="<a href=\"http://earthquaketrack.com\" rel=\"nofollow\">EarthquakeTrack.com</a>"){
    gsub("<a href=\"http://earthquaketrack.com\" rel=\"nofollow\">EarthquakeTrack.com</a>","earthquaketrack",x,fixed=TRUE)
  }else if(x=="<a href=\"http://www.didyoufeel.it/\" rel=\"nofollow\">Did You Feel It</a>"){
    gsub("<a href=\"http://www.didyoufeel.it/\" rel=\"nofollow\">Did You Feel It</a>","did_you_feel_it",x,fixed=TRUE)
  }else if(x=="<a href=\"http://www.mobeezio.com/apps/earthquake\" rel=\"nofollow\">Earthquake Mobile</a>"){
    gsub("<a href=\"http://www.mobeezio.com/apps/earthquake\" rel=\"nofollow\">Earthquake Mobile</a>","earthquake_mobile",x,fixed=TRUE)
  }else if(x=="<a href=\"http://www.facebook.com/twitter\" rel=\"nofollow\">Facebook</a>"){
    gsub("<a href=\"http://www.facebook.com/twitter\" rel=\"nofollow\">Facebook</a>","facebook",x,fixed=TRUE)
  }else {
    "others"
  }
}

finalExtractedTweets$tweetSource = sapply(finalExtractedTweets$statusSource,function(sourceSystem) encodeSource(sourceSystem))

tweetsSentiment<-sentiment(finalExtractedTweets$text)   # instead used amazondf$text 
finalExtractedTweets$polarity <- tweetsSentiment$polarity # Polarity denotes whther the tweet is neagtive, positive or neutral 

```

### Final Results for Sentiment analysis on tweets

```{r}
head(finalExtractedTweets,5)
```

### Extracting Results into excel to visualize in Tableau

```{r message=FALSE}

#write_xlsx(finalExtractedTweets,'TweetsData.xlsx')

```

## Text Analysis and Visualization

We will be first visualizing text for individual companies and generate some isnights

```{r message=FALSE }

ourCorpusMotorola =  corpus(tweetsDfMotorola,text_field = 'text')
ourCorpusXiaomi = corpus(tweetsDfXiaomi,text_field = 'text')
ourCorpusOnePlus =  corpus(tweetsDfOnePlus,text_field = 'text')
ourCorpusSamsung =  corpus(tweetsDfSamsung,text_field = 'text')

# Lets remove few stop words and punctuation

ourTokensMotorola <- tokens(ourCorpusMotorola, remove_punct = TRUE)
ourTokensXiaomi <- tokens(ourCorpusXiaomi, remove_punct = TRUE)
ourTokensOnePlus <- tokens(ourCorpusOnePlus, remove_punct = TRUE)
ourTokensSamsung <- tokens(ourCorpusSamsung, remove_punct = TRUE)

ourTokensMotorolaNS <- tokens_select(ourTokensMotorola, stopwords('en'),selection = 'remove' , min_nchar =4) 
ourTokensXiaomiNS <- tokens_select(ourTokensXiaomi, stopwords('en'),selection = 'remove' , min_nchar =4)  
ourTokensOnePlusNS <- tokens_select(ourTokensOnePlus, stopwords('en'),selection = 'remove' , min_nchar =4)  
ourTokensSamsungNS <- tokens_select(ourTokensSamsung, stopwords('en'),selection = 'remove' , min_nchar =4)  

ourMatrixMotorola <- dfm(ourTokensMotorolaNS)
ourMatrixXiaomi <- dfm(ourTokensXiaomiNS)
ourMatrixOnePlus <- dfm(ourTokensOnePlusNS)
ourMatrixSamsung <- dfm(ourTokensSamsungNS)

# Top 5 features for each company
topfeatures(ourMatrixMotorola,5)   # Motorola
topfeatures(ourMatrixXiaomi,5)     # Xiaomi
topfeatures(ourMatrixOnePlus,5)    # Oneplus 
topfeatures(ourMatrixSamsung,5)   # Samsung

# Wordcloud for most used words in the 5 companies 

textplot_wordcloud(ourMatrixMotorola,max_words = 200)  # Motorola
textplot_wordcloud(ourMatrixXiaomi,max_words = 200)    # Xiaomi
textplot_wordcloud(ourMatrixOnePlus,max_words = 200)   # Oneplus
textplot_wordcloud(ourMatrixSamsung,max_words = 200)      # Samsung
```

### Let's visualize plot for each company based on frequency of words which has been repeated atleast 10 times.

```{r message=FALSE}

# Motorola
dfmIaugMoto = dfm(ourMatrixMotorola)
dfmIaugMoto = dfm_trim(dfmIaugMoto , min_termfreq=10) 
textplot_wordcloud(dfmIaugMoto,max_words = 200 , min_size = 2)

# Xiaomi
dfmIaugXiaomi = dfm(ourMatrixXiaomi)
dfmIaugXiaomi = dfm_trim(dfmIaugXiaomi , min_termfreq=10) 
textplot_wordcloud(dfmIaugXiaomi,max_words = 200 , min_size = 2)

# Oneplus
dfmIaugOnePlus = dfm(ourMatrixOnePlus)
dfmIaugOnePlus = dfm_trim(dfmIaugOnePlus , min_termfreq=10) 
textplot_wordcloud(dfmIaugOnePlus,max_words = 200 , min_size = 2)


# Samsung
dfmIaugSamsung = dfm(ourMatrixSamsung)
dfmIaugSamsung = dfm_trim(dfmIaugSamsung , min_termfreq=10) 
textplot_wordcloud(dfmIaugSamsung,max_words = 200 , min_size = 2)

```

###  Visualization of all the 5 twitter accounts together 

```{r message=FALSE}

our_corpus <- corpus(finalExtractedTweets,text_field = 'text')
head(our_corpus,2)

# Lets remove few words and punctuation

our_tokens <- tokens(our_corpus, remove_punct = TRUE)
words_to_be_removed<-c() # Currently we are not removing any additional extra words
our_tokens_nonstopwords<- tokens_select(our_tokens, pattern = c(stopwords('en'), words_to_be_removed),selection = 'remove', min_nchar = 4)


# Document feature Matrix to show frequency of tokens in each document

our_matrix<-dfm(our_tokens_nonstopwords)
our_matrix<-dfm_trim(our_matrix, min_termfreq = 10, min_docfreq = 5)
nfeat(our_matrix) #number of tokens in all documents


#Most mentioned words

topfeatures(our_matrix,10)
topfeatures(our_matrix,30)

set.seed(42)
textplot_wordcloud(our_matrix, max_words = 200, min_size = 1, max_size = 4)  # All 5 companies combined

```
### Better Visualization of wordcloud for all the 5 companies 
```{r}
# Text plot showing visualization of all the companies together

corpus_subset(our_corpus, screenName %in% c("MotorolaUS", "Xiaomi", "oneplus","SamsungMobile")) %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(stopwords("english")) %>%
  dfm() %>%
  dfm_group(groups = screenName) %>%
  dfm_trim(min_termfreq = 5, verbose = FALSE) %>%
  textplot_wordcloud(comparison = TRUE, max_words = 200)

```
